MAESTROeX: A Massively Parallel Low Mach Number Astrophysical Solver

### 2019-09-17 MAESTROeX_I/intro.tex
fix acoustic limit statement

\explain{re-ordered discussion of other codes and approaches;
kept text intact unless indicated otherwise}
Low Mach number models \added{that do not contain acoustic waves}
have been developed for a variety of contexts
including combustion \citep{day2000numerical}, terrestrial atmospheric
modeling \citep{durran:1989,oneill:2014,duarte2015low}, and elastic
solids \citep{abbate2017all}.  
For astrophysical applications, a
number of approaches to modeling low Mach number flows have been
developed in recent years.  One of the more similar approaches to ours is
\cite{Lin:2006}, however this approach is only first-order accurate and does
not account for atmospheric expansion.
\added{There are several other approaches that retain the effects of acoustic wave 
propagation with various strategies to efficiently and robustly handle 
the low Mach number limit.}
In the reduced speed of sound technique (RSST) and related
methods, the speed of sound is artificially reduced by including a
suitable scaling factor in the continuity equation, reducing the
restriction on the size of the time step
\citep{Rempel2005,Hotta2012,Wang2015,Takeyama2017,Iijima2018}.
There are \deleted{also} semi-implicit all-Mach
number solvers, where the Euler equations are split into an acoustic
part and an advective part
\citep{Kwatra2009,Degond2009,Cordier2012,Haack2012,Happenhofer2013,Chalons2016,Padioleau2019}.
The fast acoustic waves are then solved using implicit time
integration, while the slow material waves are solved explicitly.
There are also fully implicit time integration codes for the
compressible Euler equations
\citep{kifonidis:2012,Viallet2015,Goffrey2016}.
\explain{removed outdated Viallet2011 citation and corrected the typo in the Viallet2015 citation}
The MUSIC code
uses fully implicit time integration for the compressible Euler
equations, which therefore allows for arbitrarily large time steps.
\added{To resolve potential pressure scaling issues in very low Mach number flow
in explicit or implicit schemes, }
another approach is to use preconditioned all-Mach number solvers
\citep{Miczek2014,Barsukow2016}
\added{to properly capture pressure fluctuations in the low Mach number regime
(see \citealt{guillard2017behaviour} for discussion).}
\replaced{, where}{The numerical flux is
multiplied by a preconditioning matrix}\replaced{.  This}{ that} reduces the stiffness of
the system at low Mach numbers, while retaining the correct scaling
behavior \added{in an acoustic limit of the Euler equations that 
retains $\mathcal{O}$(Ma$^2$) pressure fluctuations}.

>>>>

\explain{re-ordered discussion of other codes and approaches;
kept text intact unless indicated otherwise}
Low Mach number models \added{that do not contain acoustic waves}
have been developed for a variety of contexts
including combustion \citep{day2000numerical}, terrestrial atmospheric
modeling \citep{durran:1989,oneill:2014,duarte2015low}, and elastic
solids \citep{abbate2017all}.  
For astrophysical applications, a
number of approaches to modeling low Mach number flows have been
developed in recent years.  One of the more similar approaches to ours is
\cite{Lin:2006}, however this approach is only first-order accurate and does
not account for atmospheric expansion.
\added{There are several other approaches that retain the effects of acoustic wave 
propagation with various strategies to efficiently and robustly handle 
the low Mach number limit.}
In the reduced speed of sound technique (RSST) and related
methods, the speed of sound is artificially reduced by including a
suitable scaling factor in the continuity equation, reducing the
restriction on the size of the time step
\citep{Rempel2005,Hotta2012,Wang2015,Takeyama2017,Iijima2018}.
There are \deleted{also} semi-implicit all-Mach
number solvers, where the Euler equations are split into an acoustic
part and an advective part
\citep{Kwatra2009,Degond2009,Cordier2012,Haack2012,Happenhofer2013,Chalons2016,Padioleau2019}.
The fast acoustic waves are then solved using implicit time
integration, while the slow material waves are solved explicitly.
There are also fully implicit time integration codes for the
compressible Euler equations
\citep{kifonidis:2012,Viallet2015,Goffrey2016}.
\explain{removed outdated Viallet2011 citation and corrected the typo in the Viallet2015 citation}
The MUSIC code
uses fully implicit time integration for the compressible Euler
equations, which therefore allows for arbitrarily large time steps.
\added{To resolve potential pressure scaling issues in very low Mach number flow
in explicit or implicit schemes, }
another approach is to use preconditioned all-Mach number solvers
\citep{Miczek2014,Barsukow2016}
\added{to properly capture pressure fluctuations in the low Mach number regime
(see \citealt{guillard2017behaviour} for discussion).}
\replaced{, where}{The numerical flux is
multiplied by a preconditioning matrix}\replaced{.  This}{ that} reduces the stiffness of
the system at low Mach numbers, while retaining the correct scaling
behavior \added{in an acoustic limit of the Euler equations that 
retains $\mathcal{O}$(Ma) pressure fluctuations}.
